Network Origins of Social Distinction

### 2025-07-20 manuscript.tex
Updates from Overleaf

Where $\bar{\mathbf{\kappa}}$ is the mean of the vector of $\kappa_i$ constraint scores for each actor in the network, and $\bar{\mathbf{\kappa}}$ is the mean of the vector of $s_i$ status scores for each actor in the network. As noted a desirable feature of rescaling the $s_i$ component of equation~\ref{eq:distinction} in this way is that in the case of a regular graph (e.g., a circle graph or a fully-connected clique), $\alpha s_i = \kappa_i$ and thus $\beta_i = 0$ for each node $i$ (see Tables~\ref{tab:tab:circle} and~\ref{tab:clique}).

>>>>

Where $\bar{\mathbf{\kappa}}$ is the mean of the vector of $\kappa_i$ constraint scores for each actor in the network, and $\bar{\mathbf{\kappa}}$ is the mean of the vector of $s_i$ status scores for each actor in the network. As noted a desirable feature of rescaling the $s_i$ component of equation~\ref{eq:distinction} in this way is that in the case of a regular graph (e.g., a circle graph or a fully-connected clique), $\alpha s_i = \kappa_i$ and thus $\beta_i = 0$ for each node $i$ (see Tables~\ref{tab:circle} and~\ref{tab:clique}).
